The language of generalization: Probability, vagueness, and interaction

### 2018-03-01 paper/comgen-paper.Rmd
remove penultimate paragraph about deceit

In sum, we've tried to argue that our information-theoretic communicative model couched in our general cognitive framework can be used to explain a number of interesting and heretofore puzzling phenomena in genericity as well as make novel predictions about a wider range of language.
The precise implementation of these hypotheses we leave for future work.

@@

The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generalization that she herself would not accept, conveying a too-strong impression to a naive listener.
Our model predicts this potential particularly for properties which, when present, are widespread in a category; biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012].
Disagreements are also predicted when interlocutors fail to share background assumptions, which could manifest as differences in the prior distributions on prevalence or what goes into the comparison class.
Core aspects of political disagreement then (e.g., as to whether "Humans cause global warming") could be derived from differences in the estimated causal responsibility of the category in question (e.g., what impacts humans are having), of *other forces* (e.g., plate tectonics), as well as the comparison class of other forces (e.g., what are the alternative causes?). 
This is an important area for future research.

>>>>

In sum, we've tried to argue that our information-theoretic communicative model couched in our general cognitive framework might well explain a number of interesting and heretofore puzzling phenomena in genericity as well as make novel predictions about a wider range of language.

@@

<!-- The dark side of this flexibility is the potential for miscommunication or deceit: A speaker might assert a generalization that she herself would not accept, conveying a too-strong impression to a naive listener. -->
<!-- Our model predicts this potential particularly for properties which, when present, are widespread in a category; biological properties are believed to have this distribution, but many properties of social categories may as well [@Cimpian2011a; @Cimpian2012b; @Rhodes2012]. -->
<!-- Disagreements are also predicted when interlocutors fail to share background assumptions, which could manifest as differences in the prior distributions on prevalence or what goes into the comparison class. -->
<!-- Core aspects of political disagreement then (e.g., as to whether "Humans cause global warming") could be derived from differences in the estimated causal responsibility of the category in question (e.g., what impacts humans are having), of *other forces* (e.g., plate tectonics), as well as the comparison class of other forces (e.g., what are the alternative causes?).  -->
<!-- This is an important area for future research. -->
